SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all

### 2024-01-12 SI.tex
Editorial changes

%\pagebreak
\section*{Processing results in the application layer}

@@

%\newpage
\pagebreak
\section*{Databank content}

\begin{table}[p]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI (trr or xtc for Gromacs, dcd for OpenMM) & \\
    TPR (Gromacs) & Name of the tpr topology file found from DOI for Gromacs simulations & \\
    PDB (OpenMM) & Name of the pdb file found from DOI for OpenMM simulations & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. 
    %For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100. 
    & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. 
    %For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100. 
    & \\
    COMPOSITION & Dictionary connecting universal molecule and atom names to the ones used in simulation & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations using buildH program~\cite{santuz21}. Empty for all atom simulations. & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data & user given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication & \\
    FF\_DATE &  Date when force field parameters were accessed on the given source (day/month/year) & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD & \\
    CPT & Name of the Gromacs checkpoint file & \\
    LOG & Name of the Gromacs log file & \\
    GRO & Name of the Gromacs gro file & \\
    TOP & Name of top file for Gromacs or psf file for OpenMM & \\
    CRD & Name of crd file for OpenMM & \\
    WARNINGS & Dictionary containing information about unusual features in the trajectory, such as ambiguous atom names, membrane normal not oriented in $z$-direction, old Gromacs version used & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data \\
    TRJLENGTH & Lenght of the trajectory (ps) & \\
    TEMPERATURE & Temperature of the simulation & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation & \\
    DATEOFRUNNIG & Date when added into the Databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules in both leaflets and numbers of other molecules are added to the dictionary & \\
    ID & Unique ID number to ease the analyses & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

%\begin{table}[h]
%    \centering
%    \begin{tabular}{c|c}
%        Abbreviation & Molecule name \\
%        \hline
%        POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine\\
%        POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
%        POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
%        POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
%        CHOL & cholesterol \\
%        DHMDMAB & dihexadecyldimethylammonium \\
%        \hline
%        POT & potassium ion \\
%%        SOD & sodium ion \\
 %       CLA & chloride ion \\
%        CAL & calcium ion \\
%%    \end{tabular}
 %   \caption{Abbreviations used in the databank}
%    \label{tab:abbreviations}
%\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{  p{5.0cm}  p{10.0cm}}
    \toprule
    key & description \\
    \midrule
    DOI & DOI of the publication related to the experimental data \\
    TEMPERATURE & Temperature of the experiment \\
    MOLAR\_FRACTIONS & Dictionary of molar fractions of bilayer components \\
    ION\_CONCENTRATIONS & Dictionary of ion concentrations of the system \\
    % (defined as ??) \\
    TOTAL\_LIPID\_CONCENTRATION & Total concentration of lipid components; if exact concentration is not known, but experiments are performed in excess water, 'full hydration' can be given \\
    COUNTER\_IONS & Type of counter ions if present
\end{tabular}
    \caption{Keys stored in the README.yaml files of experiments.}
    \label{tab:READMEkeysEXP}
\end{table}

\begin{comment}

\begin{table}[p]
    \centering
    \begin{tabular}{c c}
    Abbreviation & Molecule name \\
    \hline
    Lipids and surfactants & \\
    \hline
    POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
    POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
    POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
    POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
    PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
    PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
    DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
    DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
    DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
    DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
    DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
    DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
    DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
    DOG  & 1,2-dioleoyl-sn-glycerol \\
    DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
    DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
    DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
    DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
    DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
    DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
    SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
    DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
    SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
    POPI & \\ 
    SAPI & \\
    SLPI &  \\
    SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
    SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
    CER  & N-palmitoyl-D-erythro-sphingosine \\
    CHOL & cholesterol  \\
    DCHOL & 18,19-di-nor-cholesterol \\
    DHMDMAB & dihexadecyldimethylammonium  \\
    \hline
    Other molecules & \\
    \hline
    POT & potassium ion  \\
    SOD & sodium ion  \\
    CLA & chloride ion \\
    CAL & calcium ion  \\
    CES & caesium ion \\
    SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecule names used in the Databank.}
    \label{tab:abbreviations}
\end{table}
\end{comment}

\begin{table}[p]
    \centering
    \begin{tabular}{l}
    Force field name and references \\
    \hline
    CHARMM36~\cite{klauda10}\\
    Slipids~\cite{jambeck12,jambeck12b,jambeck2012another,ermilova16,grote20}  \\
    MacRog~\cite{Kulig15b}  \\
    Amber Lipid14/17~\cite{dickson14,dickson22}  \\
    Charmm-Drude~\cite{li2017drude}      \\
    ECClipids~\cite{melcr18,melcr20,bacle21}  \\
    GROMOS-CKP~\cite{Chandrasekhar03,kukol09,piggot12}  \\
    Berger~\cite{berger97}  \\
    ECC-CHARMM36~\cite{nencini2019development}  \\
    Orange~\cite{catte16}  \\
    Poger~\cite{poger10}  \\
    GROMOS 43A1-S3~\cite{chiu09}  \\ 
    GAFFlipid~\cite{dickson12}  \\
    OPLS3e~\cite{roos19}  \\
    Ulmschneider~\cite{Ulmschneider09}  \\
    Chiu Gromos~\cite{chiu09}  \\
    AMOEBA~\cite{chu2018polarizable} \\
    OpenFF~\cite{mobley18,boothroyd23,OpenFFgit}
    \end{tabular}
    \caption{List of current force fields used in simulations in the Databank, with references.}
    \label{tab:ForceFields}
\end{table}

>>>>

\pagebreak

\section*{Databank content}

\begin{table}[!h]
    \centering
    \begin{tabular}{l}
    Force field name and references \\
    \hline
    CHARMM36~\cite{klauda10}\\Slipids~\cite{jambeck12,jambeck12b,jambeck2012another,ermilova16,grote20}  \\
    MacRog~\cite{Kulig15b}  \\
    Amber Lipid14/17~\cite{dickson14,dickson22}  \\
    Charmm-Drude~\cite{li2017drude}      \\
    ECClipids~\cite{melcr18,melcr20,bacle21}  \\
    GROMOS-CKP~\cite{Chandrasekhar03,kukol09,piggot12}  \\
    Berger~\cite{berger97}  \\
    ECC-CHARMM36~\cite{nencini2019development}  \\
    Orange~\cite{catte16}  \\
    Poger~\cite{poger10}  \\
    GROMOS 43A1-S3~\cite{chiu09}  \\ 
    GAFFlipid~\cite{dickson12}  \\
    OPLS3e~\cite{roos19}  \\
    Ulmschneider~\cite{Ulmschneider09}  \\
    Chiu Gromos~\cite{chiu09}  \\
    AMOEBA~\cite{chu2018polarizable} \\
    OpenFF~\cite{mobley18,boothroyd23,OpenFFgit}
    \end{tabular}
    \caption{List of current force fields used in simulations in the Databank, with references.}
    \label{tab:ForceFields}
\end{table}

\begin{table}[!h]
    \centering
    \begin{tabular}{  p{3.5cm}  p{9.5cm}  p{4.0cm} }
    \toprule
    key & description & type  \\
    \midrule
        %\hline
    DOI & DOI from where the raw data is found & user given (compulsory) \\
    SOFTWARE & Software used to run the simulation (Gromacs, Amber, NAMD, etc.) & \\
    TRJ & Name of the trajectory file found from DOI (trr or xtc for Gromacs, dcd for OpenMM) & \\
    TPR (Gromacs) & Name of the tpr topology file found from DOI for Gromacs simulations & \\
    PDB (OpenMM) & Name of the pdb file found from DOI for OpenMM simulations & \\
    PREEQTIME & Pre-equilibrate time simulated before the uploaded trajectory in nanoseconds. 
    %For example, if you upload 100-200 ns part of total 200 ns simulation, this should value should be 100. 
    & \\
    TIMELEFTOUT & Equilibration period in the uploaded trajectory that should be discarded in analyses. 
    %For example, if you upload 0-200 ns part of total 200 ns simulation where the first 100 ns should be considered as an equilibration, this value should be 100. 
    & \\
    COMPOSITION & Dictionary connecting universal molecule and atom names to the ones used in simulation & \\
    DIR\_WRK & Temporary working directory in your local computer. \\
    UNITEDATOM\_DICT & Information for constucting hydrogens for united atom simulations using buildH program~\cite{santuz21}. Empty for all atom simulations. & \\
    TYPEOFSYSTEM & Lipid bilayer or something else & \\
    \hline
    PUBLICATION & Give reference to a publication(s) related to the data & user given (optional)\\
    AUTHORS\_CONTACT & Name and email of the main author(s) of the data & \\
    SYSTEM & System description on free text format & \\
    SOFTWARE\_VERSION & Version of the used software & \\
    FF & Name of the used force field & \\
    FF\_SOURCE & Source of the force field parameters, e.g, CHARMM-GUI, webpage, citation to a publication & \\
    FF\_DATE &  Date when force field parameters were accessed on the given source (day/month/year) & \\
    FF{molename} & Molecule specific force field information, e.g., water model with FFSOL and sodium parameters with FFSOD & \\
    CPT & Name of the Gromacs checkpoint file & \\
    LOG & Name of the Gromacs log file & \\
    GRO & Name of the Gromacs gro file & \\
    TOP & Name of top file for Gromacs or psf file for OpenMM & \\
    CRD & Name of crd file for OpenMM & \\
    WARNINGS & Dictionary containing information about unusual features in the trajectory, such as ambiguous atom names, membrane normal not oriented in $z$-direction, old Gromacs version used & \\
    \hline
    TRAJECTORY\_SIZE & Size of the trajectory file in bytes & automatically extracted data \\
    TRJLENGTH & Lenght of the trajectory (ps) & \\
    TEMPERATURE & Temperature of the simulation & \\
    NUMBER\_OF\_ATOMS & Number of atoms in the simulation & \\
    DATEOFRUNNIG & Date when added into the Databank & \\
    EXPERIMENT & Potentially connected experimental data & \\
    COMPOSITION & Numbers of lipid molecules in both leaflets and numbers of other molecules are added to the dictionary & \\
    ID & Unique ID number to ease the analyses & \\
    \end{tabular}
    \caption{Keys stored in the README.yaml files of simulations.}
    \label{tab:READMEkeys}
\end{table}

\begin{table}[!h]
    \centering
    \begin{tabular}{  p{5.0cm}  p{10.0cm}}
    \toprule
    key & description \\
    \midrule
    DOI & DOI of the publication related to the experimental data \\
    TEMPERATURE & Temperature of the experiment \\
    MOLAR\_FRACTIONS & Dictionary of molar fractions of bilayer components \\
    ION\_CONCENTRATIONS & Dictionary of ion concentrations of the system \\
    % (defined as ??) \\
    TOTAL\_LIPID\_CONCENTRATION & Total concentration of lipid components; if exact concentration is not known, but experiments are performed in excess water, 'full hydration' can be given \\
    COUNTER\_IONS & Type of counter ions if present
\end{tabular}
    \caption{Keys stored in the README.yaml files of experiments.}
    \label{tab:READMEkeysEXP}
\end{table}

\newpage
%\pagebreak
\section*{Processing results in the application layer}

@@

%\newpage
\pagebreak
